Automated iterative near-term forecasting for the Portal Project

### 2018-02-08 manuscript/portal_iterative_forecasting_ms.Rmd
typo fix

Forecasting the future state of ecological systems is important for management, conservation, and evaluation of how well models capture the processes governing ecological systems [@clark2001; @tallis2006; @diaz2015; @dietze2017]. In 2001, Clark et al. [-@clark2001] called for a more central role of forecasting in ecology, and since then an increasing number of ecological forecasts are being published. However, most of these forecasts are made once, published, and never assessed or updated. This lack of both regular assessment and active updating has limited the progress of ecological forecasting and hindered our ability to make useful and reliable predictions. The lack of active assessment results in limited information on how much confidence to place in forecasts and makes if difficult to determine which forecasting methods to build on. Without regular updates, forecasts lack the most current data and forecast accurracy will decay over time [@petch2015; @dietze2018]. More regular updating and assessment will advance ecological forecasting as a field by accelerating the identification of the best models for individual forecasts and improving our understanding of how to best design forecasting approaches for ecology in general. For ecological forecasting to mature as a field, we need to change how we produce and interact with forecasts, creating a more dynamic interplay between model development, prediction generation, and incorporation of new data and information [@dietze2018].

>>>>

Forecasting the future state of ecological systems is important for management, conservation, and evaluation of how well models capture the processes governing ecological systems [@clark2001; @tallis2006; @diaz2015; @dietze2017]. In 2001, Clark et al. [-@clark2001] called for a more central role of forecasting in ecology, and since then an increasing number of ecological forecasts are being published. However, most of these forecasts are made once, published, and never assessed or updated. This lack of both regular assessment and active updating has limited the progress of ecological forecasting and hindered our ability to make useful and reliable predictions. The lack of active assessment results in limited information on how much confidence to place in forecasts and makes it difficult to determine which forecasting methods to build on. Without regular updates, forecasts lack the most current data and forecast accurracy will decay over time [@petch2015; @dietze2018]. More regular updating and assessment will advance ecological forecasting as a field by accelerating the identification of the best models for individual forecasts and improving our understanding of how to best design forecasting approaches for ecology in general. For ecological forecasting to mature as a field, we need to change how we produce and interact with forecasts, creating a more dynamic interplay between model development, prediction generation, and incorporation of new data and information [@dietze2018].
